Biology background

### 2014-12-11 Rmarkdown/biology_background.Rmd
CHARM

Assays based on restriction enzyme were some of the first developed for studying DNA methylation. They were initially developed for studying particular loci although they have been extended to genome-scale analysis approaches \citep{Laird:2010iv}. Restriction enzyme assays have a relatively low resolution.

>>>>

Assays based on restriction enzyme were some of the first developed for studying DNA methylation. They were initially developed for studying particular loci although they have been extended to genome-scale analysis approaches \citep{Laird:2010iv}. One such genome-wide assays is CHARM (_comprehensive high-throughput arrays for relative methylation_, \citet{Irizarry:2008hg}). CHARM combines a methylation fractionation step --- be it _MeDIP_, _HpaII_, or as in the original publication, _McrBC_ --- with a tiling array and analysis techniques that leverage regional DNA methylation levels.

While restriction enzyme assays do not typically provide single nucleotide resolution data, `methylCRF` \citep{Stevens:2013hv} is able to infer single CpG methylation levels by combining data from a restriction enzyme based assay (MRE-seq) with one based on affinity enrichment (MeDIP-seq) in a sophisticated statistical analysis.
